\sysfull

### 2017-08-12 paper/evaluation.tex
methodology patches

\subsection{Hardware Suite Description}
\label{sec:results_hardware}

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp} build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller. WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version 7. FET was also used as a power supply in non-intermittent power experiments. Energy consumption measurements provided in eariler sections were done with Carnegie Mellon's EDB~\cite{edb}. In experiments involving wireless power, the WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. The RFID reader is controlled by a PC running Ubuntu 10.4 executing an open source Python-based \emph{sllurp} library~\cite{sllrp_github}. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance-controlled experiments, the WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code execution times were measured using Salea~\cite{saleae} logic analyzer.

>>>>

\subsection{Methodology}
\label{sec:results_hardware}

We evaluated \sys using a WISP\,5.1~\cite{wisp5,wisp} energy-harvesting
platform build around a MSP430FR5969~\cite{wolverine} MCU with 64kB of FRAM.
We used a TI Flash Emulation Tool (FET)~\cite{fet} as a power supply during
experiments with continuous power.  For energy measurements, we used
EDB~\cite{edb}.  In experiments with wireless power, we powered the WISP using
an RFID reader (Impinj R1000 with firmware version
3.2.4.240~\cite{r1000_data_sheet}) connected to the Liard RFMAX S9028PCRJ
8\,dBic~\cite{atlas2015}. We ccontrolled the RFID reader from a workstation
running Ubuntu 10.4 using \emph{sllurp}~\cite{sllrp_github}.  We set the
transmitted power of the RFID reader to 30\,dBm at 915\,MHz center frequency.
For distance-controlled experiments, we affixed the WISP at varying lengths to
hollow paper tubes placed flat on a lying antenna. We did timing measurements
using the Salea~\cite{saleae} logic analyzer.
